|

### 2023-01-23 paper_comparison/paper_comparison/paper_comparison.Rmd
let lineups have the same aspect ratio as in the experiment

```{r first-example-lineup, fig.height = 7, fig.cap = "Visual testing is conducted using a lineup, as in the example here. The residual plot computed from the observed data (plot $2^2 + 2$, exhibiting non-linearity) is embedded among 19 null plots, where the residuals are simulated from a standard error model. Computing the $p$-value requires that the lineup be examined by a number of human judges, each asked to select the most different plot. A small $p$-value would result from a substantial number selecting plot $2^2 + 2$."}

@@

```{r example-poly-lineup, fig.height = 7, fig.cap = "One of the lineups containing non-linearity patterns used in experiment I. Can you spot the most different plot? The data plot is positioned at $2^3 + 1$."}
VI_MODEL$plot_lineup(vi_lineup$poly_24$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

```{r example-heter-lineup, fig.height = 7, fig.cap = "One of the lineups containing heteroskedasticity pattern used in experiment II. Can you spot the most different plot? The data plot is positioned at $3^3 - 3^2$"}

@@

```{r poly-example, eval = FALSE, fig.height = 7, fig.cap = "Example of a non-linearity that is rejected by the visual test but not by the RESET test. The data plot at panel three exhibits strong non-linear pattern. It has effect size $= 3.89$. Interestingly, all the lineups in this group are higher order polynomials (M, Triple-U), and it is apparent that the default RESET test under-performs. The RESET test using the higher order polynomial parameter could be used, but this would change it's performance for lower order polynomials. The only way for it to be sensitive to these type of departure is to know the order prior to testing!"}
# plot poly-270 
VI_MODEL$plot_lineup(vi_lineup$poly_270$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

```{r heter-example, fig.height = 7, fig.cap = 'The single heteroskedasticity lineup that is rejected by the visual test but not by the BP test. The data plot at panel 17 contains a "Butterfly" shape. It has effect size $ = 4.02$, somewhat surprising that it is not detected by the BP test.'}
# plot heter-331
VI_MODEL$plot_lineup(vi_lineup$heter_331$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

>>>>

```{r first-example-lineup, fig.height = 7, fig.width = 7, fig.cap = "Visual testing is conducted using a lineup, as in the example here. The residual plot computed from the observed data (plot $2^2 + 2$, exhibiting non-linearity) is embedded among 19 null plots, where the residuals are simulated from a standard error model. Computing the $p$-value requires that the lineup be examined by a number of human judges, each asked to select the most different plot. A small $p$-value would result from a substantial number selecting plot $2^2 + 2$."}

@@

```{r example-poly-lineup, fig.height = 7, fig.width = 7, fig.cap = "One of the lineups containing non-linearity patterns used in experiment I. Can you spot the most different plot? The data plot is positioned at $2^3 + 1$."}
VI_MODEL$plot_lineup(vi_lineup$poly_24$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

```{r example-heter-lineup, fig.height = 7, fig.width = 7, fig.cap = "One of the lineups containing heteroskedasticity pattern used in experiment II. Can you spot the most different plot? The data plot is positioned at $3^3 - 3^2$"}

@@

```{r poly-example, eval = FALSE, fig.height = 7, fig.width = 7, fig.cap = "Example of a non-linearity that is rejected by the visual test but not by the RESET test. The data plot at panel three exhibits strong non-linear pattern. It has effect size $= 3.89$. Interestingly, all the lineups in this group are higher order polynomials (M, Triple-U), and it is apparent that the default RESET test under-performs. The RESET test using the higher order polynomial parameter could be used, but this would change it's performance for lower order polynomials. The only way for it to be sensitive to these type of departure is to know the order prior to testing!"}
# plot poly-270 
VI_MODEL$plot_lineup(vi_lineup$poly_270$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

```{r heter-example, fig.height = 7, fig.width = 7, fig.cap = 'The single heteroskedasticity lineup that is rejected by the visual test but not by the BP test. The data plot at panel 17 contains a "Butterfly" shape. It has effect size $ = 4.02$, somewhat surprising that it is not detected by the BP test.'}
# plot heter-331
VI_MODEL$plot_lineup(vi_lineup$heter_331$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```
